\section{Pattern correctness}

\subsection{The differential gate earns its keep}

The single most important safety mechanism in the project is the differential
execution check. Every kernel prints a checksum of its computation, and the
harness aborts unless the baseline, the framework, and \texttt{opt -O1} all print
the same value. A transform that removes instructions but changes the answer is a
miscompile, and without this gate it would look like a great result: fewer
instructions, faster runtime, wrong output. With the gate, that outcome is a
failed run instead.

This shaped how I wrote the transforms. Every rewrite is value preserving by
construction on scalar integers, and the pass refuses to touch anything it cannot
prove safe. Floating point is the clearest example: an add of zero is not an
identity for floating point without fast math flags, because it changes the sign
of a negative zero. The simplifier never even considers it, because its
predicates only match integer constants, and a negative test pins that a floating
point add of zero survives untouched.

\subsection{Negative tests are half the suite}

For every positive rewrite there is a negative test proving the unsafe neighbor
is left alone: a multiply by a non power of two is not turned into a shift, a
volatile load is not eliminated as dead, a store and a call with effects are
kept, and two constant operands are not folded because this pass does not claim
to do constant folding. Writing these was as valuable as writing the rewrites,
because they document the exact boundary of what each pass promises, and they
would catch a future change that quietly over reached.

\subsection{Strength reduction and the wrap flags}

Turning a multiply by a power of two into a shift is only correct if the overflow
behavior is preserved. A \texttt{mul nsw} promises no signed overflow, and the
equivalent shift must carry that promise, so the pass copies the no signed wrap
and no unsigned wrap flags onto the shift it creates. A lit test checks the flags
appear on the result, not just the shift itself.
