\section{Design and Architecture}

The framework is one loadable module built from an object library that is also
linked into the unit tests, so the tests exercise exactly the code the plugin
ships. Everything lives in the \texttt{opf} namespace and separates into four
layers: analyses that read the IR, transforms that rewrite it, support code they
share, and a single registration file that names them for \texttt{opt}.

\subsection{Analyses}

Each analysis is a new pass manager function analysis returning a plain value
struct with helpers to print itself and to serialize to JSON. The same struct
feeds a human readable printer, a combined JSON emitter for the benchmark
harness, and the unit tests. Crucially, the detection predicates (is this
instruction dead, is this an algebraic identity, do these two instructions
compute the same value) are free functions rather than private methods, so the
transforms consume the identical logic. The analysis and the transform can never
disagree about what counts as a duplicate, because they call the same function.

\subsection{Transforms}

Each transform is a free function core that returns a rewrite count, wrapped by a
thin pass. Separating the core out lets the fixed point pipeline call the four
transforms directly and know whether each made progress, and lets the transforms
be unit tested without standing up a pass manager. Every transform reports a
precise \texttt{PreservedAnalyses}: it preserves the control flow graph, which it
never touches, and nothing else, because it changes instructions and values.

\subsection{The pipeline}

The \texttt{my-default} pipeline runs canonicalize, then simplify, then local
common subexpression elimination, then dead code elimination, repeating until an
iteration changes nothing or an iteration cap is reached. The order is the point:
canonicalization normalizes commutative operands so that duplicates become
visible, simplification of identities produces newly dead values, dead code
elimination removes them, and the cleanup can expose further opportunities for
the next round. A per iteration log records which pass fired and how many
rewrites it made, and whether a true fixed point was reached.
